Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
Prepare merge

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1f78b4}
\definecolor{pop2}{HTML}{33a02c}
\definecolor{pop3}{HTML}{d95f02}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}

@@

\begin{figure}\centering
  \includegraphics[width = 4.5cm]{figures/list.eps}
  \includegraphics[width = 4.5cm]{figures/textLearningCurve.eps}        
  \includegraphics[width = 4.5cm]{figures/rationalCurve.eps}   
  \caption{Learning curves for \system both with (\popp{orange}) and without
  (\pop{teal}) the recognition model. Solid lines: \% holdout testing tasks solved. Dashed lines: Average solve time.}\label{learningCurves} 
\end{figure}

@@

%\paragraph{Outlook.}
We contribute an algorithm, \systemEnding, that learns to program by
bootstrapping a DSL with new domain-specific primitives that the algorithm
itself discovers, together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration of top-down
symbolic representations and bottom-up neural networks --- both of them learned
--- helps make program induction systems more generally useful for AI. Many
directions remain open.
%\paragraph{Future.}
Two immediate goals are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here.
We are in the process of applying our algorithm to generative programs and
prototyped this with a turtle-like domain: Figure \ref{geomCompiled} gives some
preliminary results for turtle graphics  --- see supplementary material for more
details.  Another direction is to explore DSL meta-learning: can we find a
\emph{single} universal primitive set that could effectively bootstrap DSLs for
new domains, including the three domains considered,  but also many others?
}\hfill
\begin{minipage}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/geomCompiled.eps} 
  \captionof{figure}{
  Top left: Example training tasks. Top right: samples from the learned DSL.
 Bottom: learning curve  (middle), and on both sides the average sample from the DSL
  before any training (left) and after training (right). See Sec.~1 of supplement.}
\label{geomCompiled}
\end{minipage}

>>>>

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1f78b4}
\definecolor{pop2}{HTML}{33a02c}
\definecolor{pop3}{HTML}{d95f02}
\definecolor{orange}{HTML}{d95f02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\begin{figure}\centering
  \includegraphics[width = 4.5cm]{figures/list.eps}
  \includegraphics[width = 4.5cm]{figures/textLearningCurve.eps}        
  \includegraphics[width = 4.5cm]{figures/rationalCurve.eps}   
  \caption{Learning curves for \system both with (\orange{orange}) and without
  (\teal{teal}) the recognition model. Solid lines: \% holdout testing tasks solved. Dashed lines: Average solve time.}\label{learningCurves} 
\end{figure}

@@

%\paragraph{Outlook.}
We contribute an algorithm, \systemEnding, that learns to program by
bootstrapping a DSL with new domain-specific primitives that the algorithm
itself discovers, together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration of top-down
symbolic representations and bottom-up neural networks --- both of them learned
--- helps make program induction systems more generally useful for AI. Many
directions remain open.
%\paragraph{Future.}
Two immediate goals are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here.
We are in the process of applying our algorithm to generative programs and
prototyped this with a turtle-like domain: Figure \ref{geomCompiled} gives some
preliminary results for turtle graphics  --- see Section 1 of the supplementary material for more
details.  Another direction is to explore DSL meta-learning: can we find a
\emph{single} universal primitive set that could effectively bootstrap DSLs for
new domains, including the three domains considered,  but also many others?
}\hfill
\begin{minipage}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/geomCompiled.eps} 
  \captionof{figure}{
  Top left: Example training tasks. Top right: samples from the learned DSL.
 Bottom: \% holdout testing tasks solved (middle), on sides are the averaged samples from the DSL
  before any training (left) and after last iteration (right).}
\label{geomCompiled}
\end{minipage}
